Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS J08354256-0819237 and 2MASS J18212815+1414010

### 2017-01-10 ms.tex
I fixed up some text and descriptions in the appendices.

Since Equation \ref{eq:cosfit} is a poor fit to the data, as visible in Figure \ref{fig:model2Cosfit}, we also explore models with additional sinusoidal frequencies.
In the multiple term model, we add cosine functions at $n$ times the frequency:
\begin{equation}\label{eq:cosfitMultiTerm}
F(t) = B t + C + A_1 \cos(2 \pi (t - t_1)/\tau) + A_2 \cos(4 \pi (t - t_2)/\tau) + A_n \cos(2 n \pi (t - t_n)/(\tau)) +  ...
\end{equation}
Now there are $n$ amplitude parameters $A_n$ and $n$ time offset parameters $t_n$.
Figure \ref{fig:model2Cosfit} shows the best fit compared to the data for 2 term and 3 term sinusoidal fits.
We assume the same priors as the 1 term sinusoidal fit with  $A_n > 0$.
For the time offsets, we restrict the range to be $\pm$ 4 hr / $n$.
The multiple term model appear visually to fit the data well.
However, the $\bar{\chi^2}$ are still 7.9 and 7.4, so it is not the expected 1.0.
However, the error bars are underestimated when only including photon and read noise components.
With exoplanet light curves, the standard deviation of the out-of-transit baseline flux can be used as an estimate for errors. With the brown dwarf rotation light curves, there is no flat baseline over which to measure error levels.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{best_fit_multi_terms.pdf}
\caption{A zoom-in on on the time series of 2MASS J1821 in Figure \ref{fig:tserPhase1821} for the wavelength bin 1.08~$\mu$m. Error bars are shown for photon and read noise. We a best-fit models using a single cosine term (green, $\bar{\chi^2}$ = 12.1). Additional terms improve the fits to the data and the $\bar{\chi^2}$.}\label{fig:model2Cosfit}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{best_fit_spec_2temp.pdf}
\caption{Maximum likelihood spectrum using an MCMC fit to the amplitude spectrum of 2MASS J1821.}\label{fig:ML2Tempfit}
\end{centering}
\end{figure}

>>>>

Since Equation \ref{eq:cosfit} is a poor fit to the data, as visible in Figure \ref{fig:model2Cosfit}, we also explore models with additional sinusoidal frequencies.
In the multiple term model, we add cosine functions at $n$ times the frequency:
\begin{equation}\label{eq:cosfitMultiTerm}
F(t) = B t + C + A_1 \cos(2 \pi (t - t_1)/\tau) + A_2 \cos(4 \pi (t - t_2)/\tau) + A_n \cos(2 n \pi (t - t_n)/\tau) +  ...
\end{equation}
Now there are $n$ amplitude parameters $A_n$ and $n$ time offset parameters $t_n$.
Figure \ref{fig:model2Cosfit} shows the best fit compared to the data for 2 term and 3 term sinusoidal fits.
We assume the same priors as the 1 term sinusoidal fit with  $A_n > 0$.
For the time offsets, we restrict the range to be $\pm$ 4 hr / $n$.
The multiple term model appear visually to fit the data well.
However, the $\bar{\chi^2}$ are still 7.9 and 7.4, so it is not the expected 1.0.
However, the error bars are underestimated when only including photon and read noise components.
With exoplanet light curves, the standard deviation of the out-of-transit baseline flux can be used as an estimate for errors. With the brown dwarf rotation light curves, there is no flat baseline over which to measure error levels.

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{best_fit_multi_terms.pdf}
\caption{A zoom-in on on the time series of 2MASS J1821 in Figure \ref{fig:tserPhase1821} for the wavelength bin 1.08~$\mu$m. Error bars are shown for photon and read noise. We plot a best-fit models using a single cosine term (green, $\bar{\chi^2}$ = 12.1). Additional terms improve the fits to the data and the $\bar{\chi^2}$.}\label{fig:model2Cosfit}
\end{centering}
\end{figure}

@@

\begin{figure}
\begin{centering}
\includegraphics[width=0.5\textwidth]{best_fit_spec_2temp.pdf}
\caption{We repeat the amplitude spectrum of 2MASS J1821 from Figure \ref{fig:ampspec1821tdiff}, which excludes the wavelengths contaminated by telluric absorption.
We show a maximum likelihood model spectrum, which has a $\chi^2$ per degree of freedom of 1.16.}\label{fig:ML2Tempfit}
\end{centering}
\end{figure}
